Capstone Movielens Report

### 2025-05-06 reports/capstone-movielens-report.draft4.Rmd
Fix for Draft RMD report.

::: {.noteblock data-latex=""}
This code snippet is a part of the `make_source_datasets` _function_ code described above.
:::

@@

::: {.noteblock data-latex=""}
The `sample_train_validation_sets` function is defined in the same script as the `make_source_datasets` one, from where it is called.  
:::
```{r eval=FALSE}
sample_train_validation_sets <- function(data, seed){
  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
  set.seed(seed)
  validation_ind <- 
    sapply(splitByUser(data),
           function(i) sample(i, ceiling(length(i)*.2))) |> 
    unlist() |> 
    sort()

@@

@@

##### Functions to calculate _(Root) Mean Squared Error

We will need the following functions to calculate _(R)MSEs:
```{r eval=FALSE}
mse <- function(r) mean(r^2)

>>>>

::: {.noteblock data-latex=""}
This code snippet is a part of the [`make_source_datasets` _function_ code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L87) described above.
:::

@@

which returns a pair of train/validation sets:
```{r eval=FALSE}
sample_train_validation_sets <- function(data, seed){
  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
  set.seed(seed)
  validation_ind <- 
    sapply(splitByUser(data),
           function(i) sample(i, ceiling(length(i)*.2))) |> 
    unlist() |> 
    sort()

@@

::: {.noteblock data-latex=""}
The [`sample_train_validation_sets` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L15) is defined in the same script as the `make_source_datasets` one, from where it is called.  
:::

@@

##### Functions to calculate _(Root) Mean Squared Error_
\

We will need the following functions to calculate _(R)MSEs_:
```{r eval=FALSE}
mse <- function(r) mean(r^2)

### 2025-05-06 reports/capstone-movielens-report.draft4.tex
Fix for Draft RMD report.

\begin{noteblock}
This code snippet is a part of the \texttt{make\_source\_datasets}
\emph{function} code described above.

@@

\begin{noteblock}
The \texttt{sample\_train\_validation\_sets} function is defined in the
same script as the \texttt{make\_source\_datasets} one, from where it is
called.

@@

@@

\subparagraph{Functions to calculate \_(Root) Mean Squared
Error}\label{functions-to-calculate-_root-mean-squared-error}

We will need the following functions to calculate \_(R)MSEs:

>>>>

\begin{noteblock}
This code snippet is a part of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L87}{\texttt{make\_source\_datasets}
\emph{function} code} described above.

@@

which returns a pair of train/validation sets:

@@

\begin{noteblock}
The
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L15}{\texttt{sample\_train\_validation\_sets}
function} is defined in the same script as the
\texttt{make\_source\_datasets} one, from where it is called.

@@

\subparagraph{\texorpdfstring{Functions to calculate \emph{(Root) Mean
Squared
Error}}{Functions to calculate (Root) Mean Squared Error}}\label{functions-to-calculate-root-mean-squared-error}

We will need the following functions to calculate \emph{(R)MSEs}:
